\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning up

An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities. An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time. 
Fingering will occur in miscible displacments when the viscocity ratio is greater than unity. As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one. After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split. As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell. In the process, it reaches a width that is again unstable to splitting, and the pattern repeats. Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching. Important parameter is the mobility (or viscosity) ratio. This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :

>>>>

An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities. This scheme ha already been describe in detail by \citet{pavlidis2016}. An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time. 
Fingering will occur in miscible displacments when the viscocity ratio is greater than unity. As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one. After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split. As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell. In the process, it reaches a width that is again unstable to splitting, and the pattern repeats. Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching. Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
